Uncovering underlying musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and aural music skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks

### 2023-04-16 MasterThesis.tex
Updates from Overleaf

@@

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{fadings}
\usetikzlibrary{matrix, positioning}

@@

%Title parameters
\title{%
  Uncovering underlying musical content in the temporal domain \\
  \small Leveraging deep learning, inductive bias, and music aural skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks}

>>>>

\usepackage{amsfonts}
\usepackage{graphicx}

@@

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{fadings}
\usetikzlibrary{matrix, positioning}
\usetikzlibrary{shapes,arrows,positioning}

@@

%Title parameters
\title{%
  Uncovering underlying musical content in the temporal domain \\
  \small Leveraging deep learning, inductive bias, and aural music skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks}

### 2023-04-16 introduction/Subsections/Motivation.tex
Updates from Overleaf

\section{Motivation}
As a music lover, professional musician, and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them. I am deeply interested in learning how to retrieve useful embedded information within the music.

@@

I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker \cite{}, or by challenging it, as exemplified by George Russell \cite{LydianRussell}. Both approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation. Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth, development, and further understanding tonal paradigms.

>>>>

\section{Motivation}
As a music lover, professional musician, and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them. I am deeply interested in learning how to retrieve useful embedded information within music.

@@

I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker, or by challenging it, as exemplified by George Russell \cite{LydianRussell}. Both approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation. Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth, development, and further understanding tonal paradigms.

### 2023-04-16 methods/subsections/machine learning.tex
Updates from Overleaf

\item \textbf{Convolutional layers:} These layers apply a convolution operation to the input data. The convolutional layers are designed to effectively learn local patterns and features in the audio data \footnote{For a visual explanation of convolution, see this video: \url{https://youtu.be/KuXjwB4LzSA}}.

@@

\item \textbf{Fully connected layers:} These layers connect every neuron in one layer to every neuron in another, allowing the network to learn non-linear combinations of the features discovered in the previous layers. Mathematically, a fully connected layer can be represented as $Y = XW + b$, where $X$ is the input matrix, $W$ is the weight matrix, $b$ is the bias vector, and $Y$ is the output matrix. The nonlinearity is introduced through the activation function, which is applied element-wise to the output matrix, such as $Y' = f(Y)$, where $f$ represents the activation function and $Y'$ is the transformed output matrix.
\vspace*{3mm}

>>>>

\item \textbf{Convolutional layers:} These layers apply a convolution operation to the input data. The convolutional layers are designed to effectively learn local patterns and features in the audio data \footnote{For a visual explanation and further understanding of the operation convolution, see this video: \url{https://youtu.be/KuXjwB4LzSA}}.

@@

\item \textbf{Fully connected layers:} These layers connect every neuron in one layer to every neuron in another, allowing the network to learn non-linear combinations of the features discovered in the previous layers. Mathematically, a fully connected layer can be represented as $Y = XW + b$, where $X$ is the input matrix, $W$ is the weight matrix, $b$ is the bias vector, and $Y$ is the output matrix.
\vspace*{3mm}

### 2023-04-16 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

\section{Model architecture and training strategy}
Piaget's theory of cognitive development \cite{Piagets_Theory_of_Cognitive_Development} posits that children acquire knowledge from sensory and motor experiences in their early stages, from birth to around 18 months. This period, called the \textit{sensorimotor stage}, sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening. As children progress through different developmental stages until adolescence and adulthood, their reasoning progressively moves toward abstract ideas and deductive logic. Schemas, higher-order cognitive structures hypothesized to underlie many aspects of human knowledge and skill, emerge during this process, which Piaget interprets through an equilibration mechanism that balances new information with old knowledge. This mechanism involves \textit{assimilation} and \textit{accommodation}, which entail taking in further information to fit pre-existing schemas and modifying existing schemas resulting from the latest news. In the context of learning, complex structures are based on simpler ones, and knowledge transfer occurs when dynamic systems capable of generalization are created. \cite{audioselfsupsurvey}

>>>>

\section{Model architecture and training strategy}
Piaget's theory of cognitive development \cite{Huitt2003PiagetsDevelopment} posits that children acquire knowledge from sensory and motor experiences in their early stages, from birth to around 18 months. This period called the \textit{sensorimotor stage}, sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening. As children progress through different developmental stages until adolescence and adulthood, their reasoning progressively moves toward abstract ideas and deductive logic. Schemas, higher-order cognitive structures hypothesized to underlie many aspects of human knowledge and skill, emerge during this process, which Piaget interprets through an equilibration mechanism that balances new information with old knowledge. This mechanism involves \textit{assimilation} and \textit{accommodation}, which entail taking in further information to fit pre-existing schemas and modifying existing schemas resulting from the latest news. In the context of learning, complex structures are based on simpler ones, and knowledge transfer occurs when dynamic systems capable of generalization are created. \cite{audioselfsupsurvey}
